\begin{thebibliography}{}
	\vspace{4cm}
		\bibitem{RPI} Academic and Research Computing. \textit{Text Formatting with \LaTeX\ A Tutorial}. NY, April 2007.\\
				\url{http://www.rpi.edu/dept/arc/docs/latex/latex-intro.pdf}
		\bibitem{is.skills} Leslie Lamport. \textit{\LaTeX\ for Beginners}.  fifth edition, Document Reference: 3722-2014, March 2014.\\
				\url{http://www.docs.is.ed.ac.uk/skills/documents/3722/3722-2014.pdf}
		\bibitem{Tobias Oetiker} Tobias Oetiker, Hubert Partl, Irene Hyna, and Elisabeth Schlegl. \textit{The Not So Short Introduction to \LaTeX\ }. Version 6.3, March 1994.\\
				\url{https://tobi.oetiker.ch/lshort/lshort.pdf}
		\bibitem{Helmut Kopka} Helmut Kopka and Patrick W. Daly. \textit{A Guide to \LaTeX\ and Electronic Publishing}. Addison-Wesley, fourth edition, May 2003.\\
				\url{https://www2.mps.mpg.de/homes/daly/GTL/gtl_20030512.pdf}
		\bibitem{Philip Hirschhorn} Philip Hirschhorn. \textit{Using the exam document class}. Wellesley College, second edition, MA, November 2017.\\
				\url{http://www-math.mit.edu/~psh/exam/examdoc.pdf}
		\bibitem{web1} \textit{When should I use \cs{input} vs \cs{include}}.\\
				\url{https://tex.stackexchange.com/questions/246/when-should-i-use-input-vs-include}		
		\bibitem{Overleaf} Overleaf. \textit{Inserting Images}.\\
				\url{https://www.overleaf.com/learn/latex/Inserting_Images}
		\bibitem{Rice} Rice University. \textit{\LaTeX\ Mathematical Symbols}.\\
			\url{https://www.caam.rice.edu/~heinken/latex/symbols.pdf}
		\bibitem{Overleaf1} Overleaf. \textit{Integrals, sum and limits}.\\
			\url{https://www.overleaf.com/learn/latex/Integrals,_sums_and_limits}
		\bibitem{BU} Boston University. \textit{\LaTeX\ Command Summary}. December 1994.\\
			\url{https://www.bu.edu/math/files/2013/08/LongTeX1.pdf}
		\bibitem{Overleaf2} Overleaf. \textit{Subscripts and superscripts}.\\
			\url{https://www.overleaf.com/learn/latex/Subscripts_and_superscripts}
		\bibitem{Disquis} Disquis. \textit{\LaTeX\ Color}. Addison-Wesley, second edition, Reading, MA, 1994.\\
				\url{http://latexcolor.com/}
		\bibitem{David Woods} David Woods.\textit{Useful \LaTeX\ Commands}.\\
				\url{https://www.scss.tcd.ie/~dwoods/1617/CS1LL2/HT/wk1/commands.pdf}
		\bibitem{Overleaf3} Overleaf. \textit{Spacing in Math Mode}.\\
				\url{https://www.overleaf.com/learn/latex/Spacing_in_math_mode}
		\bibitem{Overleaf4} Overleaf. \textit{Fractions and Binomials}.\\
				\url{https://www.overleaf.com/learn/latex/Fractions_and_Binomials}
		\bibitem{Overleaf5} Overleaf. \textit{Environments}.\\
				\url{https://www.overleaf.com/learn/latex/Environments}
		\bibitem{Overleaf6} Overleaf. \textit{Margin Notes}.\\
				\url{https://www.overleaf.com/learn/latex/Margin_notes}
		\bibitem{Math} Art of Problem Solving. \textit{LaTeX:Commands}\\
				\url{https://artofproblemsolving.com/wiki/index.php/LaTeX:Commands}
		\bibitem{LaTeX} Latex-Project.\\
				\url{https://www.latex-project.org/about/}
		\bibitem{texstackexchange} Tex Stack Exchange. customizing part style with Tikz.\\
				\url{https://tex.stackexchange.com/questions/159551/customizing-part-style-with-tikz}
		\bibitem{texstackexchange2}	Tex Stack Exchange. How to change chapter/section style in tufte-book?.\\
				\url{https://tex.stackexchange.com/questions/83057/how-to-change-chapter-section-style-in-tufte-book?noredirect=1&lq=1}
	\end{thebibliography}
\addtocounter{section}{14}
\addcontentsline{toc}{section}{\protect\numberline{\thesection}~~~ References}